The K2 Bright Star Survey I: Methodology and Data Release

### 2019-07-15 paper/ms.tex
metcalfe citations

% describe saturation
The \kepler detector saturates at a magnitude of $K_p \sim 11.3$ in both long- (30\,min) and short (1\,min)-cadence data, since these both represent sums of 6\,s exposures \citep{Gilliland2010}. For objects brighter than this, excess electrons `bleed' into adjacent pixels in both directions along the column containing the star. Simple aperture photometry (SAP) -- adding all the flux contained in a window around the bleed column -- has recovered light curves with precisions close to the photon noise limit. Examples treated in the nominal {\it Kepler\/} mission are the prototype classical radial pulsator RR\,Lyr \citep[$V=7.2$;][]{Kolenberg2011}, the solar-like pulsators 16\,Cyg\,AB \citep[$V\approx 6$;][]{2013MNRAS.433.1262W} and $\theta\,$Cyg \citep[$V=4.48$;][]{Guzik2016}, and the massive eclipsing binary V380\,Cyg \citep[$V=5.68$;][]{tkachenko2014}. In the nominal \kepler mission SAP was only attempted for a few bright stars, and in \ktwo, the larger spacecraft motion significantly increased the size of the required apertures for SAP photometry of very saturated stars, while also making their systematics more difficult to deal with. While the second-version pixel-level-decorrelation (PLD) pipeline EVEREST~2.0 was able to correct systematics in saturated SAP photometry \citep{everest2}, this is not possible for the very brightest stars whose bleed columns may run to the edge of the detector. Furthermore, bandwidth constraints meant that pixel data were not downloaded for many bright targets in \ktwo.

>>>>

% describe saturation
The \kepler detector saturates at a magnitude of $K_p \sim 11.3$ in both long- (30\,min) and short (1\,min)-cadence data, since these both represent sums of 6\,s exposures \citep{Gilliland2010}. For objects brighter than this, excess electrons `bleed' into adjacent pixels in both directions along the column containing the star. Simple aperture photometry (SAP) -- adding all the flux contained in a window around the bleed column -- has recovered light curves with precisions close to the photon noise limit. Examples treated in the nominal {\it Kepler\/} mission are the prototype classical radial pulsator RR\,Lyr \citep[$V=7.2$;][]{Kolenberg2011}, the solar-like pulsators 16\,Cyg\,AB \citep[$V\approx 6$;][]{2012ApJ...748L..10M,2013MNRAS.433.1262W,2015ApJ...811L..37M} and $\theta\,$Cyg \citep[$V=4.48$;][]{Guzik2016}, and the massive eclipsing binary V380\,Cyg \citep[$V=5.68$;][]{tkachenko2014}. In the nominal \kepler mission SAP was only attempted for a few bright stars, and in \ktwo, the larger spacecraft motion significantly increased the size of the required apertures for SAP photometry of very saturated stars, while also making their systematics more difficult to deal with. While the second-version pixel-level-decorrelation (PLD) pipeline EVEREST~2.0 was able to correct systematics in saturated SAP photometry \citep{everest2}, this is not possible for the very brightest stars whose bleed columns may run to the edge of the detector. Furthermore, bandwidth constraints meant that pixel data were not downloaded for many bright targets in \ktwo.
